Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-08-05 analysis/paper/paper.Rmd
Added more references

---
title: "Understanding the technological transition based on cultural transmission biases during the Late Pleistocene in Korea"
author:
  - Gayoung Park
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

#library(CTtps) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory

library(here)
library(tidyverse)
```

```{r results='hide', include=FALSE}
#reading landmarks in tps, code from https://gist.github.com/mrdwab/2062329

@@

#grid.arrange(SYG6_PC1_v, SYG6_PC2_v, nrow =1)

>>>>

---
title: "Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea"
author:
  - Gayoung Park: 
      email: gayoungp@uw.edu
      institute: [UofW]
      correspondence: true
  - Ben Marwick:
      email: bmarwick@uw.edu
      institute: [UofW]
      correspondence: false

institute:
  - UofW: Department of Anthropology, University of Washington, Seattle. USA

date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r results='hide', include=FALSE}
#library(CTtps) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory

library(here)
library(tidyverse)

#reading landmarks in tps, code from https://gist.github.com/mrdwab/2062329

@@

library(gridExtra)
grid.arrange(SYG6_PC1_v, SYG6_PC2_v, nrow =1)
